Phylodynamic inference of contact network parameters through approximate Bayesian computation

### 2016-06-21 doc/thesis/intro.tex
Started writing intro for BA methods section
Almooooooost!

\add{Recall that the primary objective of our work is to develop a statistical
inference method for estimating contact network parameters from transmission
trees. For a network model with parameters $\theta$ and an input transmission
tree $T$, our goal is to estimate statistics, such as means and credible
intervals, of the posterior distribution}
\begin{align}
  \madd{\post(\theta \mid T) = \frac{\lik(T \mid \theta) \prior(\theta)}
    {\int_\Theta\lik(T \mid \theta) \prior(\theta)}.}
  \label{eq:post}
\end{align}
\add{As alluded to in \cref{sec:obj}, both the likelihood $\lik(T \mid \theta)$
and the normalizing constant are likely computationally intractable
(this will be discussed further in \cref{subsec:just}). Hence, rather than
computing the posterior distribution analytically, we will approximate it using
a \defn{Monte Carlo} approach. The fundamental idea behind Monte Carlo methods
is succinctly expressed by \textcite{liu2001theoretical}:}
\begin{quote}
    \add{Monte Carlo's view of the world is that any probability distribution
    $\pi$, regardless of its complexity, can always be \emph{represented} by a
    discrete sample from it. By ``represented'', we mean that any
    computation of expectations using $\pi$ can be replaced to an acceptable
    degree of accuracy by using the empirical distribution resulting from the
    discrete sample.}
\end{quote}
\add{In other words, if we are able to sample enough points from a distribution
of interest, we will be able to make reasonably accurate statements about the
distribution itself. For example, the expected value of the distribution can be
estimated by the sample's population mean. The reason Monte Carlo methods will
be useful in this work is that algorithms exist for obtaining samples from
distributions that are analytically intractable and from which direct sampling
is not possible (for a review see \autocite{robert2004monte}).
\Gls{SMC}~\autocite{doucet2000sequential, doucet2001introduction, liu2008monte}
is one such algorithm.}

@@

\add{Here we describe an algorithm called the \gls{SMC} sampler, developed by
\textcite{del2006sequential}, which forms the basis of the adaptive
\gls{ABC}-\gls{SMC} algorithm we apply toward the main objective of this work.
We begin by describing \gls{SIS}, which is a precursor to \gls{SMC} that
samples from a sequence of distributions defined on spaces of increasing
dimension. We then describe \gls{SMC} itself, which extends \gls{SIS} with a
resampling step to fight particle degeneracy. Finally, we outline the \gls{SMC}
sampler, which allows \gls{SMC} to be applied to sequences of distributions all
defined on the same space. This terminology will become clear as the methods
are described.}

@@

\add{The desired output of our method is a posterior distribution of the
parameters of a contact network model. Rather than assuming a homogeneously
mixed population, as most epidemiological models do, network models take the
more realistic view that human populations are structured. That is, contacts
which allow for transmission may occur in a nonrandom way, rather than between
every pair of individuals in the population. A network model parameterizes this
structure. In particular, our second research objective is to characterize our
ability to fit the \gls{BA} model, which incorporates preferential attachment
to generate networks with realistic degree distributions.}

@@

\add{Thus, our method integrates four research topics: phylogenetics, contact
networks, \acrlong{SMC}, and \acrlong{ABC}. The first two topics together form
the problem domain. Phylogenetic data is the input to our method, while
estimates of the parameters of contact network models are the desired output.
The latter two topics define the algorithm and statistical framework that our
inference method will use.}

>>>>

\add{Recall that the primary objective of our work is to develop a statistical
inference method for estimating contact network parameters from transmission
trees. For a network model with parameters $\theta$ and an input transmission
tree $T$, our goal is to estimate statistics, such as means and credible
intervals, of the posterior distribution}
\begin{align}
  \madd{\post(\theta \mid T) = \frac{\lik(T \mid \theta) \prior(\theta)}
    {\int_\Theta\lik(T \mid \theta) \prior(\theta) \d\theta}.}
  \label{eq:post}
\end{align}
\add{As alluded to in \cref{sec:obj}, both the likelihood $\lik(T \mid \theta)$
and the normalizing constant are likely computationally intractable
(this will be discussed further in \cref{subsec:just}). Hence, rather than
computing the posterior distribution analytically, we will approximate it using
a \defn{Monte Carlo} approach. The fundamental idea behind Monte Carlo methods
is succinctly expressed by \textcite{liu2001theoretical}:}
\begin{quote}
    \add{Monte Carlo's view of the world is that any probability distribution
    $\pi$, regardless of its complexity, can always be \emph{represented} by a
    discrete sample from it. By ``represented'', we mean that any
    computation of expectations using $\pi$ can be replaced to an acceptable
    degree of accuracy by using the empirical distribution resulting from the
    discrete sample.}
\end{quote}
\add{In other words, if we are able to sample enough points from a distribution
of interest, we will be able to make reasonably accurate statements about the
distribution itself. For example, the expected value of the distribution can be
estimated by the sample's population mean. The reason Monte Carlo methods will
be useful in this work is that algorithms exist for obtaining samples from
distributions that are analytically intractable and from which direct sampling
is not possible (for a review see \autocite{robert2004monte}).
\Gls{SMC}~\autocite{doucet2000sequential, doucet2001introduction, liu2008monte}
is one such algorithm.}

@@

\add{In this section, we review an algorithm called the \gls{SMC} sampler,
developed by \textcite{del2006sequential}, which forms the basis of the
adaptive \gls{ABC}-\gls{SMC} algorithm we apply toward the main objective of
this work. We begin by describing \gls{SIS}, which is a precursor to \gls{SMC}
that samples from a sequence of distributions defined on spaces of increasing
dimension. We then describe \gls{SMC} itself, which extends \gls{SIS} with a
resampling step to fight particle degeneracy. Finally, we outline the \gls{SMC}
sampler, which allows \gls{SMC} to be applied to sequences of distributions all
defined on the same space. This terminology will become clear as the methods
are described.}

@@

\add{The desired output of our method is a posterior distribution of the
parameters of a contact network model. Rather than assuming a homogeneously
mixed population, as most epidemiological models do, network models take the
more realistic view that human populations are structured. For example,
contacts may tend to occur more often between ``like'' individuals (with
respect to geometry, socioeconomic status, or other factors) than at random. A
network model provides a formal representation of this structure. In
particular, our second research objective is to characterize our ability to fit
the \gls{BA} model, which incorporates preferential attachment to generate
networks with realistic degree distributions.}

@@

\add{Thus, our method integrates four research topics: phylogenetics, contact
networks, \acrlong{SMC}, and \acrlong{ABC}. The first two topics together form
the problem domain. Phylogenetic data are the input to our method, while
estimates of the parameters of contact network models are the desired output.
The latter two topics define the algorithm and statistical framework that our
inference method will use.}

### 2016-06-21 doc/thesis/methods_results.Rnw
Almooooooost!

    m.tbl <- d[,prop.table(table(m_error))]
    zero.alpha.test <- wilcox.test(d[true_alpha == 0, alpha_error], 
                                   d[true_alpha != 0, alpha_error])
    alpha.I.test <- wilcox.test(d[true_alpha < 1, I_error],
                                d[true_alpha >= 1, I_error])
    I.I.test <- wilcox.test(d[true_I == 1000, I_error],
                            d[true_I == 2000, I_error])
    alpha.m.test <- wilcox.test(d[true_alpha == 0 | true_alpha == 1, m_error],
                                d[true_alpha == 0.5 | true_alpha == 1.5, m_error])
    #stopifnot(alpha.av["factor(true_m)", "Pr(>F)"] <= 0.05)
    #stopifnot(alpha.av["factor(true_I)", "Pr(>F)"] > 0.05)
    #stopifnot(I.I.test$p.value < 1e-5)
    #stopifnot(I.av["factor(true_m)", "Pr(>F)"] > 0.05)
    #stopifnot(m.av["factor(true_m)", "Pr(>F)"] > 0.05)
    #stopifnot(m.av["factor(true_I)", "Pr(>F)"] > 0.05)
    #stopifnot(m.av["factor(true_alpha)", "Pr(>F)"] > 0.05)
    #stopifnot(min(N.av[1:3,"Pr(>F)"]) > 0.05)

@@

\add{\Cref{fig:marginal} shows the effect of performing marginal \gls{ABC}
estimation of each of the \gls{BA} parameters on the same simulated
transmission tree. The estimates of \gls{m} are apparently unaffected by
marginalizing out the other parameters, coroborating the prevous experiments'
findings that \gls{m} is not an identifiable parameter from scaled tree shapes.
The estimates of \gls{alpha} and \gls{N} were weakly improved in marginal
estimation, which is consistent with the result from grid search that all
\gls{N} values and \gls{alpha} values below 0.5 are weakly identifiable. On the
other hand, both the accuracy and precision (\ie width of the \gls{HPD}
intervals) of the estimates of \gls{I} were substantially improved when \gls{N}
and at least one other variable were marginalized out. Neither the accuracy nor
the precision of any parameter estimates appeared to improve when more
computing power was used for \gls{SMC} (\cref{fig:moresmc}).}

@@

@@

  stopifnot(pmean1[,dataset[which.max(I)]] == "zetterberg2004")
  stopifnot(pmean1[,dataset[which.min(I)]] == "novitsky2014")
  stopifnot(pmean1[dataset != "novitsky2014", dataset[which.min(I)]] == "bctree")

  stopifnot(pmean1[,cor.test(ntip, I)$p.value, method="spearman"] > 0.05)
@

@@

\add{Posterior mean point estimates for the \acrlong{PA} power \gls{alpha}
were all sub-linear, ranging from 
    \Sexpr{pmean1["zetterberg2004", round(alpha, 2)]}
for the \gls{IDU}/Estonia data to
    \Sexpr{pmean1["cuevas2009", round(alpha, 2)]}
for the mixed/Spain data. When aggregated by risk group, the average estimates
were
    \Sexpr{pmean1[c("zetterberg2004", "niculescu2015", "bctree"), round(mean(alpha), 2)]}
for \gls{IDU},
    \Sexpr{pmean1[c("novitsky2014", "mccormack2002", "grabowski2014"), round(mean(alpha), 2)]}
for primarily heterosexual risk, and
    \Sexpr{pmean1[c("wang2015", "kao2011", "little2014", "li2015"), round(mean(alpha), 2)]}
for \gls{MSM}. These values were obtained with \textit{gag} for the datasets
where both \textit{gag} and \textit{env} were sequenced, but the estimates for
\gls{alpha} did not change appreciably between the two genes (\cref{fig:genes}).
There was a large amount of uncertainty associated with these estimates. 95\%
\gls{HPD} were very wide for most datasets, often encompassing almost the
entire range from 0 to 1 (\cref{fig:abchpd}). For all the datasets except
HET/Malawi and MSM/Beijing, the posterior mean was either outside, or very
close to the border of, the 50\% \gls{HPD}. This indicates that the posterior
distributions were diffuse with heavy tails, rather than having most of their
mass around the mode. When the value $\gls{m} = 1$ was disallowed by the prior, 
TODO}

@@

\add{For all but the HET/Botswana data, the posterior mean estimates for
the prevalence \gls{I} were between
    \Sexpr{pmean1["zetterberg2004", round(I)]}
(IDU/Estonia) and
    \Sexpr{pmean1["bctree", round(I)]}
(IDU/Canada). The HET/Botswana data had a much higher estimated \gls{I} value
    (\Sexpr{pmean1["novitsky2014", round(I)]})
than the other datasets, with a very wide 95\% \gls{HPD} interval covering
almost the entire prior region (\cref{fig:abchpd}). There was no significant
correlation between the number of sequences in the tree and the estimated
prevalence (Spearman correlation, 
    $p \Sexpr{pp(pmean1[,cor.test(ntip, I)[["p.value"]], method="spearman"], eq=TRUE)}$).
This indicates that the higher prevalence estimates were not simply due to
increased sampling density. When both \textit{gag} and \textit{env} sequences
were analyzed, the estimates from the \textit{env} data were substantially
higher (\cref{fig:genes}). The ratios of terminal to internal branch lengths
were higher for the \textit{env} trees than the \textit{gag} trees (average X
for \textit{env} and X for \textit{gag}). As with \gls{alpha}, many of the
posterior means were outside the 50\% \gls{HPD} intervals, suggesting diffuse
posterior distributions. The values of \gls{I} were largely robust to
restricting the prior to $\gls{m} > 1$ (compare
\cref{fig:abchpd,fig:abchdpm2}), although TODO}

@@

\add{The posterior means of \gls{m} were equal to one for 
  \Sexpr{replace_number(pmean1[,sum(m == 1)])}
of the datasets analysed. The widths of the 95\% \gls{HPD} varied from 0 (all
the mass on the estimated value) to 5 (the entire prior region). When the value
$\gls{m} = 1$ was disallowed by the prior, TODO.}

\add{Estimates of \gls{N} were  mostly uninformative, with very similar estimates
for all datasets (mean
    \Sexpr{pmean1[,round(mean(N))]},
range
    \Sexpr{pmean1[,round(min(N))]} - \Sexpr{pmean1[,round(max(N))]}).
This was similar to the pattern observed for the synthetic data, where the
posterior mean always fell around the upper two-thirds mark of the region
allowed by the prior. The results did not change appreciably (TODO) when the
value $\gls{m} = 1$ was assigned zero prior probability.}

To compare our results to the existing network literature, we estimated
values of the power law exponent \gls{gamma} for each of the datasets
investigated, using the posterior median estimates \del{with the prior allowing
$\gls{m} = 1$}. Because the estimates of \gls{N} were uninformative, we
simulated another set of networks with the estimated \gls{I} value, rather than
\gls{N}, as the number of nodes. The results are summarized in
\cref{tab:gamma}. All of the estimated exponents were in the range $2 \leq
\gls{gamma} \leq 2.5$, which is on the lower end of the range $2 \leq
\gls{gamma} \leq 4$ reported in the literature.

\begin{table}
    \centering
    \input{\tablepath/realdata-gamma.tex}
    \caption[
        Estimated power law exponents for six HIV datasets based on maximum
        \textit{a priori} estimates of BA model parameters.
    ]{
        Estimated power law exponents for six HIV datasets based on maximum
        \textit{a priori} estimates of BA model parameters. 100 networks were
        simulated using posterior mean parameter estimates obtained with
        \software{netabc}. The power law exponent $\gamma$ was estimated for
        each, and the median of those estimates was used as a point estimate
        for the corresponding dataset.
    }
    \label{tab:gamma}
\end{table}

>>>>

    m.tbl <- d[,prop.table(table(m_error))]
    zero.alpha.test <- wilcox.test(d[true_alpha == 0, alpha_error], 
                                   d[true_alpha != 0, alpha_error])
    alpha.I.test <- wilcox.test(d[true_alpha < 1, I_error],
                                d[true_alpha >= 1, I_error])
    I.I.test <- wilcox.test(d[true_I == 1000, I_error],
                            d[true_I == 2000, I_error])
    alpha.m.test <- wilcox.test(d[true_alpha == 0 | true_alpha == 1, m_error],
                                d[true_alpha == 0.5 | true_alpha == 1.5, m_error])

@@

\add{\Cref{fig:marginal} shows the effect of performing marginal \gls{ABC}
estimation of each of the \gls{BA} parameters on the same simulated
transmission tree. The estimates of \gls{m} are apparently unaffected by
marginalizing out the other parameters, coroborating the prevous experiments'
findings that \gls{m} is not an identifiable parameter from scaled tree shapes.
The estimates of \gls{alpha} and \gls{N} were weakly improved in marginal
estimation, which is consistent with the result from grid search that all
\gls{N} values and \gls{alpha} values below 0.5 are weakly identifiable. On the
other hand, both the accuracy and precision (\ie width of the \gls{HPD}
intervals) of the estimates of \gls{I} were substantially improved when \gls{N}
was marginalized out. Neither the accuracy nor the precision of any parameter
estimates appeared to improve when more computing power was used for \gls{SMC}
(\cref{fig:moresmc}).}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{abc-marginal.pdf}
    \caption[
        Marginal posterior mean estimates and 50\%/95\% \gls{HPD} intervals of
        \gls{BA} model parameters when some parameters were fixed.
    ]{
        Marginal posterior mean estimates (points), 50\% \gls{HPD} intervals
        (notches), and 95\% \gls{HPD} intervals (lines) of \gls{BA} model
        parameters when some parameters ($x$-axis) were fixed. Parameters were
        fixed by specifying a Dirac-delta prior at the true value. True values
        are indicated by horizontal dashed lines.
    }
    \label{fig:marginal}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{stock/missing}
    \caption[
        Comparsion of \gls{BA} parameter estimates obtained with
        \software{netabc} on the same dataset with different \gls{SMC}
        settings.
    ]{
        Comparsion of \gls{BA} parameter estimates obtained with
        \software{netabc} on the same dataset with different \gls{SMC}
        settings. Points are posterior means, notches are 50\% \gls{HPD}
        intervals, and lines are 95\% \gls{HPD} intervals.
    }
    \label{fig:moresmc}
\end{figure}

@@

  setkey(d1, dataset)
  setkey(d2, dataset)
  setkey(d1.env, dataset)
  setkey(d2.env, dataset)

  pmean1 <- unique(d1)[,.(dataset, ntip)][pmean1]
  pmean2 <- unique(d2)[,.(dataset, ntip)][pmean2]
  pmean1.env <- unique(d1.env)[,.(dataset, ntip)][pmean1.env]
  pmean2.env <- unique(d2.env)[,.(dataset, ntip)][pmean2.env]

@@

  stopifnot(pmean1[,dataset[which.min(I)]] == "zetterberg2004")
  stopifnot(pmean1[,dataset[which.max(I)]] == "novitsky2014")
  stopifnot(pmean1[dataset != "novitsky2014", dataset[which.max(I)]] == "bctree")

  stopifnot(pmean1[,cor.test(ntip, I, method="spearman")$p.value] > 0.05)
@

@@

\add{Posterior mean point estimates for the \acrlong{PA} power \gls{alpha}
were all sub-linear, ranging from 
    \Sexpr{pmean1["zetterberg2004", round(alpha, 2)]}
for the \gls{IDU}/Estonia data to
    \Sexpr{pmean1["cuevas2009", round(alpha, 2)]}
for the mixed/Spain data. When aggregated by risk group, the average estimates
were
    \Sexpr{pmean1[c("zetterberg2004", "niculescu2015", "bctree"), round(mean(alpha), 2)]}
for \gls{IDU},
    \Sexpr{pmean1[c("novitsky2014", "mccormack2002", "grabowski2014"), round(mean(alpha), 2)]}
for primarily heterosexual risk, and
    \Sexpr{pmean1[c("wang2015", "kao2011", "little2014", "li2015"), round(mean(alpha), 2)]}
for \gls{MSM}. These values were obtained with \textit{gag} for the datasets
where both \textit{gag} and \textit{env} were sequenced, but the estimates for
\gls{alpha} did not change appreciably between the two genes (\cref{fig:genes}).
There was a large amount of uncertainty associated with these estimates. 95\%
\gls{HPD} were very wide for most datasets, often encompassing almost the
entire range from 0 to 1 (\cref{fig:abchpd}). For all the datasets except
HET/Malawi and MSM/Beijing, the posterior mean was either outside, or very
close to the border of, the 50\% \gls{HPD}. This indicates that the posterior
distributions were diffuse with heavy tails, rather than having most of their
mass around the mode. When the value $\gls{m} = 1$ was disallowed by the prior, 
the separation between the \gls{IDU} datasets and the others became more
striking (\cref{fig:abchpdm2}). All three \gls{IDU} datasets had estimated
\gls{alpha} values at or above
    \Sexpr{pmean2[c("zetterberg2004", "niculescu2015", "bctree"), round(min(alpha), 2)]}.
The estimate for the MSM/Beijing data was slightly lower
    (\Sexpr{pmean2["wang2015", round(alpha, 2)]}) and
the estimates for the seven remaining non-\gls{IDU} datasets were bounded above by
    \Sexpr{pmean2[c("novitsky2014", "mccormack2002", "grabowski2014", "kao2011", "little2014", "li2015", "cuevas2009"), round(max(alpha), 2)]}.}

@@

<<genetrees, include=FALSE>>=
    datasets <- c("grabowski2014", "zetterberg2004", "mccormack2002")
    paths <- paste0("../../simulations/", datasets, "/subtree/*")
    paths <- sapply(paths, Sys.glob)
    trees <- lapply(paths, read.tree)
    get.ratio <- function (t) {
        int <- t$edge.length[t$edge[,2] > Ntip(t)]
        tip <- t$edge.length[t$edge[,2] <= Ntip(t)]
        mean(int) / mean(tip)
    }
    ratios <- data.table(dataset=rep(datasets, each=2),
                         gene=rep(c("env", "gag"), 3),
                         ratio=sapply(trees, get.ratio))
    stopifnot(ratios[gene == "env", mean(ratio)] <
              ratios[gene == "gag", mean(ratio)])
@

\add{For all but the HET/Botswana data, the posterior mean estimates for
the prevalence \gls{I} were between
    \Sexpr{pmean1["zetterberg2004", round(I)]}
(IDU/Estonia) and
    \Sexpr{pmean1["bctree", round(I)]}
(IDU/Canada). The HET/Botswana data had a much higher estimated \gls{I} value
    (\Sexpr{pmean1["novitsky2014", round(I)]})
than the other datasets, with a very wide 95\% \gls{HPD} interval covering
almost the entire prior region (\cref{fig:abchpd}). There was no significant
correlation between the number of sequences in the tree and the estimated
prevalence (Spearman correlation, 
    $p \Sexpr{pp(pmean1[,cor.test(ntip, I, method="spearman")[["p.value"]]], eq=TRUE)}$),
indicating that the higher prevalence estimates were not simply due to
increased sampling density. When both \textit{gag} and \textit{env} sequences
were analyzed, the estimates from the \textit{env} data were substantially
higher (\cref{fig:genes}). The ratios of internal to terminal branch lengths
were lower for the \textit{env} trees than the \textit{gag} trees (average 
    \Sexpr{ratios[gene == "env", round(mean(ratio), 2)]}
for \textit{env} and 
    \Sexpr{ratios[gene == "gag", round(mean(ratio), 2)]}
for \textit{gag}). As with \gls{alpha}, many of the posterior means were
outside the 50\% \gls{HPD} intervals, suggesting diffuse posterior
distributions. The values of \gls{I} were fairly robust to restricting the
prior to $\gls{m} \geq 2$ (compare \cref{fig:abchpd,fig:abchdpm2}), although 
the 95\% \gls{HPD} intervals were slightly narrower (average width
    \Sexpr{round(mean(up1[,I] - low1[,I]))}
for $\gls{m} \geq 1$ and
    \Sexpr{round(mean(up2[,I] - low2[,I]))}
for $\gls{m} \geq 2$).}

@@

\add{The posterior means of \gls{m} were equal to one for 
  \Sexpr{replace_number(pmean1[,sum(m == 1)])}
of the datasets analysed. The widths of the 95\% \gls{HPD} intervals varied
from 0 (all the mass on the estimated value) to 5 (the entire prior region).
When the value $\gls{m} = 1$ was disallowed by the prior, the posterior means
for all but the HET/Botswana data took on the value 3, with the \gls{HPD}
intervals spanning the entire prior region. This is very similar to the results 
observed for \gls{m} on simulated data (\cref{fig:abcptm2,tab:abchpd}), and
suggests that \gls{m} is not identifiable from these data with this prior. On
the other hand, the estimate and 95\% \gls{HPD} interval for the HET/Botswana
data (4 [2-5]) was the same for both priors.}

\add{Estimates of \gls{N} were  mostly uninformative, with very similar estimates
for all datasets (mean
    \Sexpr{pmean1[,round(mean(N))]},
range
    \Sexpr{pmean1[,round(min(N))]} - \Sexpr{pmean1[,round(max(N))]}).
This was similar to the pattern observed for the synthetic data, where the
posterior mean always fell around the upper two-thirds mark of the region
allowed by the prior. The results did not change appreciably when the value
$\gls{m} = 1$ was assigned zero prior probability.}

To compare our results to the existing network literature, we estimated
values of the power law exponent \gls{gamma} for each of the datasets
investigated, using the posterior median estimates \del{with the prior allowing
$\gls{m} = 1$}. The results are summarized in \cref{tab:gamma}. All of the
estimated exponents were in the range $2 \leq \gls{gamma} \leq 2.5$, which is
on the lower end of the range $2 \leq \gls{gamma} \leq 4$ reported in the
literature. \add{Because the estimates of \gls{N} were uninformative, we also
simulated another set of networks with the estimated \gls{I} value, rather than
\gls{N}, as the number of nodes. However, none of the estimated \gls{gamma}
values were changed by this operation (not shown).}

\begin{table}
    \centering
    \input{\tablepath/realdata-gamma.tex}
    \caption[
        Estimated power law exponents for six \gls{HIV} datasets based on
        posterior mean point estimates of \gls{BA} model parameters.
    ]{
        Estimated power law exponents for six \gls{HIV} datasets based on
        posterior mean point estimates of \gls{BA} model parameters. 100
        networks were simulated using posterior mean parameter estimates
        obtained with \software{netabc}. The power law exponent \gls{gamma}
        was estimated for each, and the median of those estimates was used as a
        point estimate for the corresponding dataset.
    }
    \label{tab:gamma}
\end{table}
